Distributional Trees and Forests

### 2017-06-28 pkg/disttree/inst/useR2017/slides.Rnw
changed plot size of example tree
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1496 255f4249-2263-4417-b1ea-8498779e27a7

\begin{frame}
\frametitle{Fitting a Tree}
\vspace*{-0.1cm}
\begin{center} 
DGP:  $\; Y\ |\ X = x \; \sim  \; \mathcal{N}(\mu(x), \sigma^2(x))$
\vspace*{-0.21cm}
<<dgp_tree, echo=FALSE, results=hide>>=
data <- data.frame(x = numeric(0), x = numeric(0), x = numeric(0))
names(data) <- c("x","x","x")
fig <- party(
  partynode(1L,
            split = partysplit(2L, breaks = 0.4),
            kids = list(
              partynode(2L, info = c(
                "n = 200",
                "   True parameters:   ",
                expression(mu == '4'),
                expression(sigma == '1')
              )),
              partynode(3L,
                        split = partysplit(3L, breaks = 0.8),
                        kids = list(
                          partynode(4L, info = c(
                            "n = 200",
                            "   True parameters:   ",
                            expression(mu == '12'),
                            expression(sigma == '3')
                          )),
                          partynode(5L, info = c(
                            "n = 100",
                            "   True parameters:   ",
                            expression(mu == '4'),
                            expression(sigma == '3')
                          )))))),
  data
)

@@

\setkeys{Gin}{width=0.65\linewidth, height=0.65\linewidth}
<<plottree_dgp, fig=TRUE, echo=FALSE>>=
paltrees <- rgb(c(0.97, 0.64, 1), c(0.70, 0.83, 1), c(0.30, 0.99, 1))
plot(fig, inner_panel = node_inner_ext,
     tp_args = list(FUN = identity, width = 18, fill = paltrees[c(1, 3)]), 
     ip_args = list(fill = paltrees[c(2, 3)]),
     drop_terminal = TRUE, tnex = 1.7)
@
\end{center}
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.1cm}
Model: \code{disttree(y ~ x)}\\
\vspace*{-0.2cm}
\setkeys{Gin}{width=0.65\linewidth, height=0.65\linewidth}
<<plottree_estpar, fig=TRUE, echo=FALSE>>=
# function for output in terminal panels
FUN <- function (x) 
{
  cf <- x$coefficients
  cf <- matrix(cf, ncol = 1, dimnames = list(names(cf), ""))
  c(sprintf("n = %s", x$nobs), "Estimated parameters:", parse(text = paste0("mu == '", format(round(cf[1], 2), nsmall = 2), "'")), 
                                                        parse(text = paste0("sigma == '", format(round(cf[2], 2), nsmall = 2), "'")))
}

@@

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.1cm}
Model: \code{disttree(y ~ x)}\\
\vspace*{-0.2cm}
\setkeys{Gin}{width=0.65\linewidth, height=0.65\linewidth}
<<plottree_box, fig=TRUE, echo=FALSE>>=
plot(as.constparty(tree), tnex = 1.7, drop = TRUE,
     tp_args = list(fill = paltrees[c(1, 3)], ylines = 1.5), 
     ip_args = list(fill = paltrees[c(2, 3)]))
@
\end{center}
\end{frame}

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.1cm}
Model: \code{disttree(y ~ x)}\\
\vspace*{-0.2cm}
\setkeys{Gin}{width=0.65\linewidth, height=0.65\linewidth}
<<plottree_dens, fig=TRUE, echo=FALSE>>=
node_density <- function (tree, xscale = NULL, yscale = NULL, horizontal = FALSE,
                          main = "", xlab = "", ylab = "Density", id = TRUE, rug = TRUE,
                          fill = paltrees[c(1, 3)], col = "black", lwd = 0.5, ...) 
{
  yobs <- tree$data[,as.character(tree$info$formula[[2]])]
  ylines <- 1.5
  if (is.null(xscale)) xscale <- c(-5.1,22.5)
  if (is.null(yscale)) yscale <- c(-0.05,0.5)
  xr <- xscale
  yr <- yscale

>>>>

\begin{frame}
\frametitle{Fitting a Tree}
\vspace*{-0.12cm}
\begin{center} 
DGP:  $\; Y\ |\ X = x \; \sim  \; \mathcal{N}(\mu(x), \sigma^2(x))$
\vspace*{-0.21cm}
<<dgp_tree, echo=FALSE, results=hide>>=
data <- data.frame(x = numeric(0), x = numeric(0), x = numeric(0))
names(data) <- c("x","x","x")
fig <- party(
  partynode(1L,
            split = partysplit(2L, breaks = 0.4),
            kids = list(
              partynode(2L, info = c(
                "n = 200",
                "   True parameters:   ",
                expression(mu == '4'),
                expression(sigma == '1')
              )),
              partynode(3L,
                        split = partysplit(3L, breaks = 0.8),
                        kids = list(
                          partynode(4L, info = c(
                            "n = 200",
                            "   True parameters:   ",
                            expression(mu == '12'),
                            expression(sigma == '3')
                          )),
                          partynode(5L, info = c(
                            "n = 100",
                            "   True parameters:   ",
                            expression(mu == '4'),
                            expression(sigma == '3')
                          )))))),
  data
)

@@

\setkeys{Gin}{width=0.68\linewidth, height=0.68\linewidth}
<<plottree_dgp, fig=TRUE, echo=FALSE>>=
paltrees <- rgb(c(0.97, 0.64, 1), c(0.70, 0.83, 1), c(0.30, 0.99, 1))
plot(fig, inner_panel = node_inner_ext,
     tp_args = list(FUN = identity, width = 18, fill = paltrees[c(1, 3)]), 
     ip_args = list(fill = paltrees[c(2, 3)]),
     drop_terminal = TRUE, tnex = 1.7)
@
\end{center}
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.12cm}
Model: \code{disttree(y ~ x)}\\
\vspace*{-0.2cm}
\setkeys{Gin}{width=0.68\linewidth, height=0.68\linewidth}
<<plottree_estpar, fig=TRUE, echo=FALSE>>=
# function for output in terminal panels
FUN <- function (x) 
{
  cf <- x$coefficients
  cf <- matrix(cf, ncol = 1, dimnames = list(names(cf), ""))
  c(sprintf("n = %s", x$nobs), "Estimated parameters:", parse(text = paste0("mu == '", format(round(cf[1], 2), nsmall = 2), "'")), 
                                                        parse(text = paste0("sigma == '", format(round(cf[2], 2), nsmall = 2), "'")))
}

@@

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.12cm}
Model: \code{disttree(y ~ x)}\\
\vspace*{-0.2cm}
\setkeys{Gin}{width=0.68\linewidth, height=0.68\linewidth}
<<plottree_box, fig=TRUE, echo=FALSE>>=
plot(as.constparty(tree), tnex = 1.7, drop = TRUE,
     tp_args = list(fill = paltrees[c(1, 3)], ylines = 1.5), 
     ip_args = list(fill = paltrees[c(2, 3)]))
@
\end{center}
\end{frame}

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.12cm}
Model: \code{disttree(y ~ x)}\\
\vspace*{-0.2cm}
\setkeys{Gin}{width=0.68\linewidth, height=0.68\linewidth}
<<plottree_dens, fig=TRUE, echo=FALSE>>=
node_density <- function (tree, xscale = NULL, yscale = NULL, horizontal = FALSE,
                          main = "", xlab = "", ylab = "Density", id = TRUE, rug = TRUE,
                          fill = paltrees[c(1, 3)], col = "black", lwd = 0.5, ...) 
{
  yobs <- tree$data[,as.character(tree$info$formula[[2]])]
  ylines <- 1.5
  if (is.null(xscale)) xscale <- c(-5.1,22.5)
  if (is.null(yscale)) yscale <- c(-0.05,0.5)
  xr <- xscale
  yr <- yscale
